\documentclass[line]{latex_lib/resume}

\usepackage{pifont} 
\usepackage{verbatim}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.5in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.11in}}}{\end{list}}
      
\newenvironment{list2}{
  \begin{list}{$-$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.175in}}}{\end{list}
}


\newcounter{itemcounter}

\newenvironment{list3}{
  \begin{list}{\arabic{itemcounter}.}{\usecounter{itemcounter}\leftmargin=0.15in}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      }}{\end{list}
}



\begin{document}

\name{\huge Prantik Bhattacharyya}  %\vspace*{.05in}}

\begin{resume}
\section{\sc \bf Contact Information}
\begin{ncolumn}{2}
San Francisco 	&   {\it Phone:} 123-456-7890\\ 
California, USA &   {\it Github:} https://github.com/\verb+~+prantik\\ 
\end{ncolumn}

\section{\sc \bf Research Interests}
Software Development, Large Scale Data Analysis, 
Social Search Engines, Social Network Theory.

\section{\sc \bf Education}
\begin{list1}
\item Ph.D., Computer Science, University of California, Davis \hfill{\it{July. 2012}} 
\begin{list2}
\item Thesis title: Search and Analysis of User Keywords in Online Social Networks
\end{list2}
\end{list1}

\begin{list1}
\item M.S., Computer Science,  University of California, Davis \hfill{\it{Sep. 2007 - Dec. 2009}}
\end{list1}

\begin{list1}
\item B.E., Computer Science and Engineering, Jadavpur University, India \hfill{\it{Jul. 2003 - Jun. 2007}}
\end{list1}


\section{\sc \bf Technical Skills} 
\begin{list2}
\item Languages:  Scala, Python, Java, MySQL
\item	Web Technologies: JSON, XML, HTML
\item	Big data computing technologies: Hadoop, Hive, HBase, Storm
\item	Web application framework: Play! 
\item Operating Systems: Linux, Mac OS X, Windows 
\end{list2}


\section{\sc \bf Experience}

\begin{list1}
\item {\bf Software Engineer, Klout} \hfill {\it{Aug. 2012 - Present}}

\begin{list2}
\item Large scale data collection frameworks to collect social interactions spread across multiple social media platforms.
\item	Develop real-time pipeline infrastructure for processing social feeds, feature extraction and analysis of internet scale-data.
\end{list2}
\end{list1}


\begin{list1}
\item {\bf Graduate Student Researcher, University of California Davis} \hfill {\it{Jul. 2008 - Present}}
\begin{list1}
\item[]
Adviser: Prof. S. (Shyhtsun) Felix Wu, Computer Science Department\\
\end{list1}

\begin{list2}
\item Developed \textit{InfoSearch}, a social search engine based on Facebook Platform. [\ref{prantik-rank11}] 
\item Validated the relationship between user similarity and social network topology. [\ref{prantik-snam10}]
\end{list2}
\end{list1}


\section{\sc \bf Publications}
\begin{list3}
\item{\label{prantik-rank11} {Prantik Bhattacharyya}, and Shyhtsun Felix Wu. \textit{InfoSearch: A Social Search Engine.} To appear in Recent Advances in Data mining: Methodologies, Challenges and Opportunities, 2013.}

\item{\label{prantik-snam10}  {Prantik Bhattacharyya}, Ankush Garg, and S. Felix Wu. \textit{Analysis of User Keyword Similarity in Online Social Networks.} In Social Networks Analysis and Mining Journal (by Springer), 2010.}
\end{list3}

\section{\sc \bf Talks}
\begin{list2}
\item \textit{Social Network Model based on Keyword Categorization.} In ASONAM '09: International Conference on Advances in Social Network Analysis and Mining, Athens, Greece, July 2009.
\end{list2}

\section{\sc \bf References}
%Available upon request.   
\begin{tabular}{lll}
S. (Shyhtsun) Felix Wu,  & & Travis Lybbert \\
Professor, Computer Science, &  & Professor, Agricultural \& Resource Economics, \\
University of California, Davis, &  & University of California, Davis, \\
Email: wu@cs.ucdavis.edu & & Email: tlybbert@ucdavis.edu
\end{tabular}

\end{resume}
\end{document}
